\documentclass[a4paper, 12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames, dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks, pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\definecolor{Primary}{RGB}{179, 13, 13}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\color{Primary}\raggedright\large
}{}{0em}{}[\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small #1
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Start
\begin{document}

% Heading
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://nurlan.co/}{\Large Nurlan Suyundukov}} & Email : \href{mailto:hi@nurlan.co}{hi@nurlan.co}\\
  \href{https://nurlan.co/}{https://nurlan.co} & Mobile : +7 925 591-01-58 \\
\end{tabular*}

% Education
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Université Claude Bernard Lyon 1}{Lyon, France}
      {Coursework toward a Bachelor of Computer Science}{Sep 2014 -- Jun 2017}
  \resumeSubHeadingListEnd

% Experience
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {GetTransfer.com}{Larnaca, Cyprus}
      {Lead Frontend Developer}{Sep 2020 -- Present}
      \resumeItemListStart
        \resumeItem{Responsible for writing clean code, product planning, driving technical design and owning technical delivery.}
        \resumeItem{Mentored junior and senior engineers on best practices in full stack development.}
        \resumeItem{Participated in interviewing and recruiting candidates.}
        \resumeItem{Performed bug fixes and code reviews.}
      \resumeItemListEnd
      Technologies used: JavaScript, Vue.js, Node.js, HTML/CSS, SCSS, Capacitor, Memcached.

    \resumeSubheading
      {GetTransfer.com}{Moscow, Russia}
      {Frontend Developer}{Jun 2019 -- Sep 2020}
      \resumeItemListStart
        \resumeItem{Performed front-end development for all projects.}
        \resumeItem{Ensured scalability of front end elements by optimizing them for loading speed and performance.}
        \resumeItem{Collaborated with web designers, back end developers and UX designers to design, build, test and improve web products.}
        \resumeItem{Supervise junior developers, provide training and motivate team members.}
      \resumeItemListEnd
      Technologies used: JavaScript, Vue.js, Node.js, HTML/CSS, SCSS, Capacitor

    \resumeSubheading
      {SprintMaster Ltd. (m7.su)}{Moscow, Russia}
      {Frontend Developer}{Oct 2018 -- Jun 2019}
      \resumeItemListStart
        \resumeItem{Build stable and maintainable codebases using React.}
        \resumeItem{Implemented a mobile-first approach to existing websites.}
        \resumeItem{Collaborated with designers to ensure designs were efficient and technically sound.}
        \resumeItem{Implemented HTML email templates and newsletters for marketing campaigns.}
      \resumeItemListEnd
      Technologies used: TypeScript, React, Redux, HTML/CSS, SCSS, GraphQL, Capacitor

  \resumeSubHeadingListEnd

% Programming Skills
\section{Programming Skills}
 \resumeSubHeadingListStart
    \item \textbf{Languages}{: Go, JavaScript, Python, TypeScript}
    \item \textbf{Technologies}{: React, Vue, Node.js, Git, JQuery, HTML, CSS}
    \item \textbf{Other}{: PostgreSQL, Redis, Memcached}
 \resumeSubHeadingListEnd

% Miscellaneous
\section{Miscellaneous}
  \resumeSubHeadingListStart
    \item Languages: English, French, Russian
 \resumeSubHeadingListEnd

 \end{document}
